---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.path = "man/figures/README-",
  comment = "#>"
)
library(ggquiver)
library(dplyr)
```

[![Travis-CI Build Status](https://travis-ci.org/mitchelloharawild/ggquiver.svg?branch=master)](https://travis-ci.org/mitchelloharawild/ggquiver)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/ggquiver)](https://cran.r-project.org/package=ggquiver)
[![Downloads](http://cranlogs.r-pkg.org/badges/ggquiver?color=brightgreen)](https://cran.r-project.org/package=ggquiver)

# ggquiver

Quiver plots for ggplot2. An extension of 'ggplot2' to provide quiver plots to 
visualise vector fields. This functionality is implemented using a geom to 
produce a new graphical layer, which allows aesthetic options. This layer can 
be overlaid on a map to improve visualisation of mapped data.

## Installation

The **stable** version can be installed from CRAN:

```{r, eval = FALSE}
install.packages("ggquiver")
```

The **development** version can be installed from GitHub using:

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("mitchelloharawild/ggquiver")
```

## Usage

*ggquiver* introduces a new geom `geom_quiver()`, which produces a quiver plot in *ggplot2*.

Quiver plots for functions can easily be produced using ggplot aeshetics. When a grid is detected, the size of the vectors are automatically adjusted to fit within the grid.

```{r quiverplot}
library(ggplot2)
library(ggquiver)
expand.grid(x=seq(0,pi,pi/12), y=seq(0,pi,pi/12)) %>%
  ggplot(aes(x=x,y=y,u=cos(x),v=sin(y))) +
  geom_quiver()
```

The *ggplot2* example for seal movements is easily reproduced, with appropriately scaled arrowhead sizes. Here, the vecsize is set to zero to not resize the vectors.

```{r sealplot}
ggplot(seals, aes(x=long, y=lat, u=delta_long, v=delta_lat)) + 
  geom_quiver(vecsize=0) + 
  borders("state")
```

Quiver plot arrows can be centered about x and y coordinates, which is useful when working with maps and scaled vectors.

```{r windplot, message=FALSE}
library(ggmap)
library(dplyr)

wind_data <- wind %>% filter(between(lon, -96, -93) & between(lat, 28.7, 30))
qmplot(lon, lat, data=wind_data, extent="panel", geom = "blank", zoom=8, maptype = "toner-lite") + 
  geom_quiver(aes(u=delta_lon, v=delta_lat, colour = spd), center=TRUE)
```


